Who does big team science?

### 2023-11-01 manuscript_scopus.Rmd
adding one more sentence

```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region. Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel). Slopes included both the overall value of the predictor ($b$, $b_M$) and the standard deviation of the predictor over time ($b_{SD}$). The color of the square represents the strength of the predictor. The top figure represents all results together for comparison across analyses. The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions. Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
graph_overall <- graph_data %>% 
  bind_rows(graph_data_2) %>% 
  bind_rows(graph_data_3) %>% 
  mutate(type = factor(type, levels = c("Effect Size", "SD Coefficient", "Coefficient"))) %>% 
  mutate(Estimate = estimate) %>% 
  mutate(heat_label = ifelse(
    low < .00001 & high > .00001, "NS", ""
  ))

>>>>

```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region. Each square represents a *b* value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis $R^2$. Slopes included both the overall value of the predictor ($b$, $b_M$) and the standard deviation of the predictor over time ($b_{SD}$). The color of the square represents the strength of the predictor. The top figure represents all results together for comparison across analyses. The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions. Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
graph_overall <- graph_data %>% 
  bind_rows(graph_data_2) %>% 
  bind_rows(graph_data_3) %>% 
  mutate(type = factor(type, levels = c("Effect Size", "SD Coefficient", "Coefficient"))) %>% 
  mutate(Estimate = estimate) %>% 
  mutate(heat_label = ifelse(
    low < .00001 & high > .00001, "NS", ""
  ))

### 2023-11-01 manuscript_scopus.tex
adding one more sentence

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-heatmap-1.pdf}
\caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region. Each square represents a \emph{b} value or the slope of the predictor (x-axis) onto the dependent variable (each panel). Slopes included both the overall value of the predictor (\(b\), \(b_M\)) and the standard deviation of the predictor over time (\(b_{SD}\)). The color of the square represents the strength of the predictor. The top figure represents all results together for comparison across analyses. The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions. Non-significant results are indicated with NS on the plot.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-heatmap-1.pdf}
\caption{\label{fig:fig-heatmap}Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region. Each square represents a \emph{b} value or the slope of the predictor (x-axis) onto the dependent variable (each panel), with the exception of the bottom row which is the effect size of each regression analysis \(R^2\). Slopes included both the overall value of the predictor (\(b\), \(b_M\)) and the standard deviation of the predictor over time (\(b_{SD}\)). The color of the square represents the strength of the predictor. The top figure represents all results together for comparison across analyses. The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions. Non-significant results are indicated with NS on the plot.}
\end{figure}
